---
title: "GMC Models II - Revised"
author: "Alexander Murph"
date: "11/6/2016"
output: html_document
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
library("grid")
library("MASS")
library(gplots)
library(ggplot2)
library(neuralnet)
library(ROCR)
library(rpart)
library(rpart.plot)
library("e1071")
library(caret)
library(pROC)
```

```{r, echo = FALSE}
data_frame = read.csv("GMC_Complete_Data2.csv")
data_frame = data_frame[,-1]
head(data_frame, 10)

data_frame$Septic_Date = as.factor(data_frame$Septic_Date)
levels(data_frame$Septic_Date) = c('C1','C2')

trainIndex <- createDataPartition(data_frame$Septic_Date,p=0.7,list=F)
training_data <- data_frame[trainIndex,]
testing_data <- data_frame[-trainIndex,]

```

```{r results = 'hide'}
train_control <- trainControl(method = "cv", number=10,savePredictions = T,summaryFunction = twoClassSummary,classProbs = T)

linearModel <- train(Septic_Date ~., data=training_data, trControl=train_control, method="glm",metric="ROC")

annModel <- train(Septic_Date ~., data=training_data, trControl=train_control, method="nnet",metric="ROC",maxit=1000)

treeModel <- train(Septic_Date ~., data=training_data, trControl=train_control, method="rpart1SE",metric="ROC")

svmModel <- train(Septic_Date ~., data=training_data, trControl=train_control, method="svmLinear2",metric="ROC")

```

## Predicting Septic Shock from Sepsis with Linear Model

This model uses the full cleaned data set. Using a logistic regression model, and the variables



```{r, echo = FALSE, warning = FALSE}
set.seed(5)
my_sample = sample(1:nrow(data_frame), ceiling(nrow(data_frame)*0.7) )
training_data = data_frame[my_sample,]
testing_data = data_frame[-my_sample,]


#linear_model = glm(Septic_Date ~ ., data = training_data, family = "binomial")


```

we predict the onset of Septic Shock (yes or no).

```{r, echo = FALSE, warning = FALSE, message = F}

#preds = predict(linear_model, type = "response", newdata = testing_data)
# preds <- ifelse(preds > 0.5,1,0)


library(ROCR)

# p <- predict(linear_model, newdata= testing_data, type="response")
# pr <- prediction(p, testing_data$Septic_Date)
# prf <- performance(pr, measure = "tpr", x.measure = "fpr")
# plot(prf, col = 'purple')
# 
# auc <- performance(pr, measure = "auc")
# auc <- auc@y.values[[1]]
# auc

predData <- predict(linearModel,testing_data,type="prob")
annROC <- roc(testing_data$Septic_Date, predData$C1)
plot(annROC)


```

# Predicting Septic Shock from Sepsis with Decision Tree Model

This model uses the full cleaned data set. Using a decision tree model, and the variables

```{r, echo = FALSE, warning = FALSE, message = F}
library(rpart)
library(ggplot2)
library(rpart.plot)
```

```{r}
rpart_model = treeModel

```

we predict the onset of Septic Shock (yes or no).  Also, because I think it is pretty, I included the visual of the decision tree.

```{r, echo = FALSE, warning=FALSE}

predData <- predict(treeModel,testing_data,type="prob")
annROC <- roc(testing_data$Septic_Date, predData$C1)
plot(annROC)

```

## Predicting Septic Shock from Sepsis with Support Vector Machine Model

This model uses the full cleaned data set. Using a svm, and the variables  

```{r, echo = FALSE, warning=FALSE, message = F}
library("e1071")

# svm_model = best.svm(Septic_Date ~., data = training_data)

svm_model = svmModel

```

we predict the onset of Septic Shock (yes or no).

```{r, echo = FALSE, warning=FALSE}
predData <- predict(svmModel,testing_data,type="prob")
annROC <- roc(testing_data$Septic_Date, predData$C1)
plot(annROC)
```

## Predicting Septic Shock with ANN


```{r, echo = FALSE, warning = FALSE}

set.seed(25)
index = sample(1:nrow(data_frame), ceiling(nrow(data_frame)*0.7) )
data_frame$Septic_Date = as.numeric(data_frame$Septic_Date)

maxs <- apply(data_frame, 2, max) 
mins <- apply(data_frame, 2, min)

scaled <- as.data.frame(scale(data_frame, center = mins, scale = maxs - mins))

train_ <- scaled[index,]
test_ <- scaled[-index,]
```

```{r}
n <- names(train_)
f <- as.formula(paste("Septic_Date ~", paste(n[-10], collapse = " + ")))
```

```{r, message=F, warning=F}
nn = annModel

```


```{r, message=F, warning=F, echo = F, fig.width = 10, fig.height = 5}
library(devtools)
source_url('https://gist.githubusercontent.com/fawda123/7471137/raw/466c1474d0a505ff044412703516c34f1a4684a5/nnet_plot_update.r')

plot.nnet(nn) 
```

```{r}
# p <- predict(annModel, newdata= testing_data, type="raw")
# pr <- prediction(p, testing_data$Septic_Date)
# prf <- performance(pr, measure = "tpr", x.measure = "fpr")
# plot(prf, col = 'purple')
# 
# auc <- performance(pr, measure = "auc")
# auc <- auc@y.values[[1]]
# auc

predData <- predict(annModel,testing_data,type="prob")
annROC <- roc(testing_data$Septic_Date, predData$C1)
plot(annROC)
```



